Data organization in spreadsheets

### 2017-08-26 manuscript.Rmd
Add example of a feature that doesn't work with plain text

Also note that, if your Excel file *did* contain critical features
that will not work when saved as a plain text file,
that is a problem.
For your primary data file, keep things simple.

>>>>

Also note that, if your Excel file *did* contain critical features that will not
work when saved as a plain text file, such as highlighted cells, that is a
problem; those features *will* be lost. For your primary data file, keep things
simple.
